Lawrence Bull, PhD

### 2024-04-02 index.qmd
glasgow

**[2022-2027] University of Cambridge** | [Computational Statistics and Machine Learning Group](https://csml-cam.github.io) | Research Associate | Department of Engineering

**[2021-2022] The Alan Turing Institute** | Research Associate | [Data-Centric Engineering](https://www.turing.ac.uk/research/research-programmes/data-centric-engineering)

**[2016-2021] University of Sheffield** | PhD Student (2016-2019) Research Assistant (2019-2022) | [Dynamics Research Group](https://drg.ac.uk/) | Department of Engineering

@@

Broadly speaking, I'm a researcher in statistical methods for Data-Centric Engineering. Focussing on monitoring techniques for telemetry data from systems and infrastructure.

I'm particularly interested in _multilevel structures_ that appear in measurements from populations of systems -- trains, [planes](https://www.sciencedirect.com/science/article/pii/S0022460X21001449), [automobiles](https://doi.org/10.48550/arXiv.2204.12404) (... [wind turbines](https://arxiv.org/abs/2111.15496)).
By encoding domain expertise in a Bayesian workflow, complex models can be built from interpretable units, allowing machines to share information and increasing the value of data.
At the population level, alternative insights can emerge that might otherwise be missed -- the whole is something _besides_ its parts.

I'm a communications editor for the [Data-Centric Engineering](https://www.cambridge.org/core/journals/data-centric-engineering) journal (Cambridge University Press) and a member of the [Early-Career Academic and Professionals Panel](https://www-smartinfrastructure.eng.cam.ac.uk/news/csic-call-applicants-early-career-academics-and-professionals-panel) (ECAPP) in the [Cambridge Centre for Smart Infrastructure and Construction](https://www-smartinfrastructure.eng.cam.ac.uk/) (CSIC).

>>>>

**[May.2024-May.2027] University of Glasgow** | Research Fellow | [Statistics & Data Analytics](https://www.gla.ac.uk/schools/mathematicsstatistics/research/stats/ai3/) | School of Mathematics and Statistics

**[Sep.2022-May.2024] University of Cambridge** | Research Associate | [Computational Statistics and Machine Learning Group](https://csml-cam.github.io) | Department of Engineering

**[Jul.2021-Sep.2022] The Alan Turing Institute** | Research Associate | [Data-Centric Engineering](https://www.turing.ac.uk/research/research-programmes/data-centric-engineering)

**[Sep.2016-Jun.2021] University of Sheffield** | PhD Student (2016-2019) Research Assistant (2019-2021) | [Dynamics Research Group](https://drg.ac.uk/) | Department of Engineering

@@

Researcher in statistical methods for Data-Centric Engineering, specialising in monitoring techniques for telemetry data from systems and infrastructure.

I'm interested in the dependencies that appear in measurements from populations of machines -- [planes](https://www.sciencedirect.com/science/article/pii/S0022460X21001449), [trains](https://arxiv.org/abs/2403.17820), [automobiles](https://doi.org/10.48550/arXiv.2204.12404) (... [wind turbines](https://arxiv.org/abs/2111.15496)).
By encoding domain expertise into statistical models, complex representations can be built from interpretable units, allowing machines to share information and increase the value of data.
<!-- At a systems level, alternative insights can emerge that might otherwise be missed -- the whole is something _besides_ its parts. -->

I'm a communications editor for the [Data-Centric Engineering](https://www.cambridge.org/core/journals/data-centric-engineering) journal and a Visiting Research Fellow at [Cambridge University](https://csml-cam.github.io). I was on the [Early-Career Academic and Professionals Panel](https://www-smartinfrastructure.eng.cam.ac.uk/news/csic-call-applicants-early-career-academics-and-professionals-panel) (2021-2023) in the [Cambridge Centre for Smart Infrastructure and Construction](https://www-smartinfrastructure.eng.cam.ac.uk/) (CSIC).
